%TeX

\documentclass{amsbook}

\usepackage[top=0.25in,bottom=0.25in,left=0.125in,right=0.125in]{geometry}
\usepackage[letterspace=150]{microtype}
\usepackage[utf8]{inputenc}
\usepackage[overload]{textcase}
\usepackage{mdframed}
\usepackage{setspace}
\usepackage{xspace}
\usepackage{pgfkeys}
\usepackage{etoolbox}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{ifoddpage}
\usepackage[none]{hyphenat}

\usepackage{luacode}

\usepackage{wizpen}

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\geometry{
    paperheight=9.75in,
    paperwidth=7.5in,
}

\setlength\parindent{0pt}

\newcommand{\LuaSpellbook}{require('lua/spellbook')}

\luadirect{tex.print(table.concat(\LuaSpellbook.preamble(), ''))}

\newcommand{\SpellbookMatch}[4]{%
    \luadirect{tex.print(\LuaSpellbook.match(\luastring{#1}, \luastring{#2}, \luastringN{#3}, \luastringN{#4}))}%
}

\newcommand{\SpellbookCleanup}[1]{%
    \luadirect{tex.print(\LuaSpellbook.cleanup(\luastringN{#1}))}%
}

\newcommand{\SpellbookDice}[1]{%
    \luadirect{tex.print(\LuaSpellbook.dice(\luastring{#1}))}%
}

\newcommand{\SpellbookDiceTwoArg}[2]{%
    \textcolor{red}{#1d#2}\xspace%
}

\newcommand{\SpellbookDiceFourArg}[4]{%
    \textcolor{red}{%
        #1d#2\enspace{\normalfont\textcolor{black}{\raisebox{3pt}{#3}}\enspace}#4%
    }\xspace%
}

\newcommand{\SpellbookDistanceOneArg}[1]{%
    \textcolor{cyan}{#1 foot}\xspace%
}

\newcommand{\SpellbookRangeTwoArg}[2]{%
    \textcolor{ForestGreen}{#1}%
    \enspace{\normalfont\raisebox{3pt}{/}}\enspace%
    \textcolor{ForestGreen}{#2}\xspace%
}

\newcommand{\SpellTimeColor}[2]{%
    \SpellbookMatch{#1}{action}{\textcolor{purple}}{%
        \SpellbookMatch{#1}{bonus}{\textcolor{cyan}}{%
            \SpellbookMatch{#1}{reaction}{\textcolor{red}}{%
                \textcolor{black}%
            }%
        }%
    }%
    #2%
}

\newcommand{\SpellEffortColor}[2]{%
    \SpellbookMatch{#1}{ritual}{\textcolor{cyan}}{%
        \SpellbookMatch{#1}{concentration}{\textcolor{red}}{%
            \textcolor{black}%
        }%
    }%
    #2%
}

\newcommand{\SpellRangeColor}[2]{%
    \SpellbookMatch{#1}{self}{\textcolor{purple}}{%
        \SpellbookMatch{#1}{touch}{\textcolor{cyan}}{%
            \textcolor{black}%
        }%
    }%
    #2%
}

\newcommand{\SpellDurationColor}[2]{%
    \SpellbookMatch{#1}{instant}{\textcolor{purple}}{%
        \SpellbookMatch{#1}{round}{\textcolor{cyan}}{%
            \SpellbookMatch{#1}{minute}{\textcolor{red}}{%
                \textcolor{black}%
            }%
        }%
    }%
    #2%
}

\newcommand{\SpellMakeType}[3]{%
    % type, save, damage
    \SpellbookMatch{#1}{save}{%
        \textcolor{cyan}{\MakeTextUppercase{#2} \SpellbookDice{#3}} ~\\ ~\\ %
    }{%
        \SpellbookMatch{#1}{attack}{%
            \ifdefempty{#3}{ }{\textcolor{red}{\SpellbookDice{#3}} ~\\ ~\\} %
        }{%
            \ifdefempty{#3}{ }{\SpellbookDice{#3} ~\\ ~\\}%
        }%
    }%
}

\newcommand{\SpellMakeMaterials}[2]{%
    \SpellbookMatch{#1}{m}{%
        \begin{mdframed}%
            \begin{centering}%
                \textcolor{red}{Components required} \\%
                \hrulefill ~\\ ~\\%
            \end{centering}%
            \begin{centering}%
                \begin{sloppypar}%
                    \SpellbookCleanup{#2}%
                \end{sloppypar}%
            \end{centering}%
        \end{mdframed}%
    }{ }%
}

\pgfkeys{
    /Spell/.is family, /Spell,
    level/.estore in = \SpellLevel,
    components/.estore in = \SpellComponents, % v/s/m combinations
    effort/.estore in = \SpellEffort, % spell/ritual/concentration
    effort/.default = spell,
    duration/.estore in = \SpellDuration, % instant/n rounds/n minutes
    time/.estore in = \SpellTime, % action/bonus/reaction/something else
    school/.estore in = \SpellSchool,
    range/.estore in = \SpellRange, % self/touch/something else
    type/.estore in = \SpellType, % automatic/save/attack
    type/.default = auto,
    save/.estore in = \SpellSave, % dex/wis/con/etc
    save/.default = ,
    damage/.estore in = \SpellDamage, % damage dice
    damage/.default = ,
    materials/.estore in = \SpellMaterials, % description, sadly w/o commas
    materials/.default = ,
    text/.store in = \SpellTextPrefix, % anything to prefix text with
    text/.default = \empty,
}

\newcommand{\Spell}[3][] {%
    \pgfkeys{/Spell, effort, type, save, damage, materials, text, #1}%
    \checkoddpage%
    \ifoddpage%
    {%
        \huge \renewcommand{\baselinestretch}{1.5}%
        {\wizpenfont #2} \hfill%
            {\wizpenfont \SpellEffortColor{\SpellEffort}{\SpellComponents}}%
            {\Huge \enspace \raisebox{3pt}{\rom{\SpellLevel}}} \\ \\%
        {\wizpenfont \SpellDurationColor{\SpellDuration}{\SpellDuration}} \hfill%
            {\wizpenfont \SpellTimeColor{\SpellTime}{\SpellTime}} \\ \\%
        {\wizpenfont \SpellSchool} \hfill%
            {\wizpenfont \SpellRangeColor{\SpellRange}{\SpellRange}} \\%
    }%
    \else%
    {%
        \huge \renewcommand{\baselinestretch}{1.5}%
        {\Huge \raisebox{3pt}{\rom{\SpellLevel}} \enspace}%
        {\wizpenfont \SpellEffortColor{\SpellEffort}{\SpellComponents}} \hfill%
            {\wizpenfont #2} \\ \\%
        {\wizpenfont \SpellTimeColor{\SpellTime}{\SpellTime}} \hfill%
            {\wizpenfont \SpellDurationColor{\SpellDuration}{\SpellDuration}} \\ \\%
        {\wizpenfont \SpellRangeColor{\SpellRange}{\SpellRange}} \hfill%
            {\wizpenfont \SpellSchool} \\%
    }%
    \fi%
    {%
        \huge%
        \begin{center}%
            {\wizpenfont \SpellMakeType{\SpellType}{\SpellSave}{\SpellDamage}}
        \end{center}%
    }%
    {%
        \LARGE \renewcommand{\baselinestretch}{1}%
        {%
            \wizpenfont%
            \begin{sloppypar}%
                \SpellTextPrefix%
                \SpellbookCleanup{#3}%
            \end{sloppypar}%
        } ~\\%
    }%
    {%
        \LARGE%
        {\wizpenfont \SpellMakeMaterials{\SpellComponents}{\SpellMaterials}}%
    }%
    \clearpage
}

\begin{document}
\pagenumbering{gobble}
{
    \Spell[%
        level=1, school=evocation, type=save, save=dex, damage=3d6, time=action,
        range=self, components=vs, duration=instant
    ]{Burning Hands}{
        As you hold your hands with thumbs touching and fingers spread, a thin 
        sheet of flames shoots forth from your outstretched fingertips. Each 
        creature in a 15-foot cone must make a Dexterity saving throw. A 
        creature takes 3d6 fire damage on a failed save, or half as much damage 
        on a successful one. The fire ignites any flammable objects in the area 
        that aren't being worn or carried.

        At Higher Levels. When you cast this spell using a spell slot of 2nd 
        level or higher, the damage increases by 1d6 for each slot level above 
        1st.
    }
    \Spell[%
        level=1, school=enchantment, type=save, save=wis, time=action,
        range=30 feet, components=vs, duration=1 hour
    ]{Charm Person}{
        You attempt to charm a humanoid you can see within range. It must make a 
        Wisdom saving throw, and does so with advantage if you or your 
        companions are fighting it. If it fails the saving throw, it is charmed 
        by you until the spell ends or until you or your companions do anything 
        harmful to it. The charmed creature regards you as a friendly 
        acquaintance. When the spell ends, the creature knows it was charmed by 
        you.

        When you cast this spell using a spell slot of 2nd 
        level or higher, you can target one additional creature for each slot 
        level above 1st. The creatures must be within 30 feet of each other when 
        you target them.
    }
    \Spell[%
        level=1, school=abjuration, time=action, range=touch,
        components=vsm, materials=a piece of cured leather, duration=8 hours
    ]{Mage Armor}{
        You touch a willing creature who isn't wearing armor, and a protective 
        magical force surrounds it until the spell ends. The target's base AC 
        becomes 13 + its Dexterity modifier. The spell ends if the target dons 
        armor or if you dismiss the spell as an action.
    }
    \Spell[%
        level=1, school=evocation, damage=1d4+1, time=action,
        range=120 feet, components=vs, duration=instant
    ]{Magic Missile}{
        You create three glowing darts of magical force. Each dart hits a 
        creature of your choice that you can see within range. A dart deals 1d4 
        + 1 force damage to its target. The darts all strike simultaneously, and 
        you can direct them to hit one creature or several.

        At Higher Levels. When you cast this spell using a spell slot of 2nd 
        level or higher, the spell creates one more dart for each slot level 
        above 1st.
    }
    \Spell[%
        level=1, school=abjuration, time=reaction, range=self,
        components=vs, duration=1 round
    ]{Shield}{
        An invisible barrier of magical force appears and protects you. Until 
        the start of your next turn, you have a +5 bonus to AC, including 
        against the triggering attack, and you take no damage from magic 
        missile.

        Reaction: take when you are hit by an attack or targeted by the magic
        missile spell
    }
    \Spell[%
        level=1, school=conjuration, time=1 hour, range=10 feet,
        components=vsm, materials=10 gp worth of charcoal; incense; and herbs
        that must be consumed by fire in a brass brazier,
        duration=instant, effort=ritual, text=\small
    ]{Find Familiar}{
        You gain the service of a familiar, a spirit that takes an animal form 
        you choose: bat, cat, crab, frog (toad), hawk, lizard, octopus, owl, 
        poisonous snake, fish (quipper), rat, raven, sea horse, spider, or 
        weasel. Appearing in an unoccupied space within range, the familiar has 
        the statistics of the chosen form, though it is a celestial, fey, or 
        fiend (your choice) instead of a beast.

        Your familiar acts independently of you, but it always obeys your 
        commands. In combat, it rolls its own initiative and acts on its own 
        turn. A familiar can't attack, but it can take other actions as normal. 
        When the familiar drops to 0 hit points, it disappears, leaving behind 
        no physical form. It reappears after you cast this spell again. While 
        your familiar is within 100 feet of you, you can communicate with it 
        telepathically. Additionally, as an action, you can see through your 
        familiar's eyes and hear what it hears until the start of your next 
        turn, gaining the benefits of any special senses that the familiar has. 
        During this time, you are deaf and blind with regard to your own senses. 
        As an action, you can temporarily dismiss your familiar. It disappears 
        into a pocket dimension where it awaits your summons. Alternatively, you 
        can dismiss it forever. As an action while it is temporarily dismissed, 
        you can cause it to reappear in any unoccupied space within 30 feet of 
        you. You can't have more than one familiar at a time. If you cast this 
        spell while you already have a familiar, you instead cause it to adopt a 
        new form. Choose one of the forms from the above list. Your familiar 
        transforms into the chosen creature.

        %Finally, when you cast a spell with a range of touch, your familiar can 
        %deliver the spell as if it had cast the spell. Your familiar must be 
        %within 100 feet of you, and it must use its reaction to deliver the 
        %spell when you cast it. If the spell requires an attack roll, you use 
        %your attack modifier for the roll.
    }
    \Spell[%
        level=1, school=illusion, time=1 minute, range=touch,
        components=sm, materials=lead ink worth at least 10 gp,
        duration=10 days, effort=ritual, text=\large
    ]{Illusory Script}{
        You write on parchment, paper, or some other suitable writing material 
        and imbue it with a potent illusion that lasts for the duration. To you 
        and any creatures you designate when you cast the spell, the writing 
        appears normal, written in your hand, and conveys whatever meaning you 
        intended when you wrote the text. To all others, the writing appears as 
        if it were written in an unknown or magical script that is 
        unintelligible. Alternatively, you can cause the writing to appear to be 
        an entirely different message, written in a different hand and language, 
        though the language must be one you know.

        Should the spell be dispelled, the original script and the illusion both 
        disappear. A creature with truesight can read the hidden message.
    }
    \Spell[%
        level=2, school=conjuration, time=bonus, range=self,
        components=v, duration=instant
    ]{Misty Step}{
        Briefly surrounded by silvery mist, you teleport up to 30 feet to an 
        unoccupied space that you can see.
    }
    \Spell[%
        level=2, school=necromancy, type=attack, time=action, range=60 feet,
        components=vs, duration=1 minute, effort=concentration
    ]{Ray of Enfeeblement}{
        A black beam of enervating energy springs from your finger toward a 
        creature within range. Make a ranged spell attack against the target. On 
        a hit, the target deals only half damage with weapon attacks that use 
        Strength until the spell ends.

        At the end of each of the target's turns, it can make a Constitution 
        saving throw against the spell. On a success, the spell ends.
    }
    \Spell[%
        level=2, school=illusion, time=action, range=touch,
        components=vsm, materials=an eyelash encased in gum arabic,
        duration=1 hour, effort=concentration
    ]{Invisibility}{
        A creature you touch becomes invisible until the spell ends. Anything 
        the target is wearing or carrying is invisible as long as it is on the 
        target's person. The spell ends for a target that attacks or casts a 
        spell.

        At Higher Levels. When you cast this spell using a spell slot of 3rd 
        level or higher, you can target one additional creature for each slot 
        level above 2nd.
    }
    \Spell[%
        level=2, school=conjuration, damage=3d6, time=bonus, range=touch,
        components=vsm, materials=hot pepper, duration=1 minute,
        effort=concentration
    ]{Dragon's Breath}{
        Touch a willing creature. Choose acid, cold, fire, lightning, or poison. 
        Until the spell ends, the creature can use an action to exhale energy of 
        the chosen type in a 15 foot cone. Each creature in that area must make 
        a Dexterity save, taking 3d6 damage on a failed save, or half as much on 
        a success.
    }
    \Spell[%
        level=2, school=illusion, damage=2d8, time=bonus, range=self,
        components=vs, duration=1 minute, effort=concentration
    ]{Shadow Blade}{
        You create a magic sword that lasts until the spell ends. It counts as a 
        simple melee weapon that you're proficient with. It deals 2d8 psychic 
        damage, and has the finesse, light, and thrown properties (range 20/60). 
        When you attack in dim light or darkness, you have advantage.

        If you drop the weapon or throw it, it disappears at the end of the 
        turn. While the spell lasts, you can use a bonus action to make the 
        sword reappear in your hand.

        At Higher Levels: When you cast this spell using a 3rd or 4th level 
        slot, the damage is 3d8. At 5th or 6th level, it's 4d8. At 7th level or 
        higher, it's 5d8.
    }
}

\end{document}

